\chapter{Ethical Considerations}

% PARA 1 -- past performance is not indicative of future results
While the trading strategies backed by machine learning models presented in this report may produce favourable results, these strategies are presented for research purposes only. Therefore the research presented in this report should not be relied upon as a basis on which to make investment decisions. Past performance of these strategies is not indicative of future results. Strategies should be paper traded before decisions are made. \\ \\
Algorithmic trading, and futures trading in particular incur a substantial exposure to risk. Since futures trading involves leverage, investors have the ability to access large futures contracts (i.e gain exposure) with a relatively small `initial margin'. This may increase the chances of margin calls, thus amplifying one's losses. Careful consideration about risk management is required when trading futures. Particularly inexperienced investors should not be exposed to these futures trading strategies. \\ \\
It should be noted that changes in economic and political regimes, whether local or global, can severely impact futures markets with unexpected behaviour. Such situations may have perverse effects on the performance of the futures trading strategies presented. Investors should acknowledge the limitations of algorithmic trading in this scenario. \\ \\
The graphs and data presented in this report may be misinterpreted by less competent practitioners. Captions and explanations within this report will provide clarity and detail about the implications of the data generated during the course of this project.  \\ \\
Handling and interpreting results of evaluating trading strategies presents some challenges, therefore code and theory will be carefully inspected to ensure that strategies are simulated in environments that model real financial markets appropriately.
